The Astropy Project

### 2017-10-17 main.tex
Update on Overleaf.

\begin{abstract}
% I (Adrian) took a first stab at the abstract, but it needs some work. Feel
% free to modify!
The \astropy project supports and fosters the development of open-source
\python packages that provide commonly-needed functionality to the astronomical
community.
A key element of the project is the \astropy core package, which serves as the
foundation for more specialized projects and packages.
In this article, we provide an overview of the organization of the \astropy
project and summarize key features in the core package as of the recent major
release, version 2.0.
We then describe the project infrastructure designed to facilitate and support
development for a broader ecosystem of interoperable packages.
We conclude with a future outlook of planned new features and directions for the
broader \astropy project.
\end{abstract}

@@

\subsection{Coordinates}
\label{sec:coordinates}
% Adrian, Erik
\inlinecomment{APW}{Do we want to put in a PDF of the transform graph?}
\inlinecomment{EJT}{I think so?  It looks pretty slick...}

>>>>

\begin{abstract}
% I (Adrian) took a first stab at the abstract, but it needs some work. Feel
% free to modify!
The \astropy project supports and fosters the development of open-source
\python packages that provide commonly-needed functionality to the astronomical
community.
A key element of the project is the \astropy core package, which serves as the
foundation for more specialized projects and packages.
In this article, we provide an overview of the organization of the \astropy
project and summarize key features in the core package as of the recent major
release, version 2.0.
We then describe the project infrastructure designed to facilitate and support
development for a broader ecosystem of inter-operable packages.
We conclude with a future outlook of planned new features and directions for the
broader \astropy project.
\end{abstract}

@@

\subsection{Coordinates}
\label{sec:coordinates}
% Adrian, Erik
